Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-16 paper/paper.tex
Improvements to the paragraphs about the second and third shadow rendering methods.

Suppose you have a pair of proceedures that are used to efficiently check whether a line segment intersects a sphere or a cylinder. You can iterate over the lights, and over all the pixels in the image, and construct the line segment from the light to the center of the pixel. Then go through all the spheres and cylinders checking for an intersection. At the first intersection, the light intensity at the pixel is decremented and we move on to the next pair of a light and a pixel. The motivation behind this method is that there is no step of merging the shadow of each point light source. [Consider writing out pseudo code for this.]

@@

@@

It should also be very fast to render shadows using openGL. Shadowmaps are a standard technique for rendering dynamic shadows. In shadowmapping, a scene is rendered from the perspective of a point light source and the resulting ``image'' is colored according to how far each part of the image is from the light. Shadowmapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall.

>>>>

Suppose you have a pair of proceedures that are used to efficiently check whether a line segment intersects a sphere or a cylinder. You can iterate over the lights, and over all the pixels in the image, and construct the line segment from the light to the center of the pixel. Then go through all the spheres and cylinders checking for an intersection. At the first intersection, the light intensity at the pixel is decreased by a fraction of its maximum value and we move on to the next pair of a light and a pixel. The motivation behind this method is that it is not necessary to merge the shadow of each point light source, a step that is a substantial time-waster in the first method.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{clumping_figure.png}
    \caption{dfsd}
    \label{fig:shadow_2}
\end{figure}

@@

It should also be very fast to render shadows using openGL. Shadowmaps are a standard technique for rendering dynamic shadows. In shadowmapping, a scene is rendered from the perspective of a point light source and the resulting ``image'' is colored according to how far each part of the image is from the light. Shadowmapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall. Therefore we would instead iterate over the pixels in the image and compare the depth of each to the calculated depth at the relevant point in the shadow map. If the depths match to within some approximation then that pixel is unshadowed, and inversely, if they differ, the pixel is shadowed. That this lighting method is dynamic is advantageous because the shadow will have to be rendered with respect to multiple point light sources. Like the first method, this method has the downside of requiring that the shadows from each light be averaged.
